Parsing Postfix log files

### 2007-07-09 doc/logparser.tex
Updated the coverage section to reflect progress on reducing warnings and state table entries.

At the time of writing the parser is being tested with 93 log files.  There
are 25 warnings produced, but because the parser errs on the side of
producing more warnings rather than fewer those 25 warnings represent only
8 problems:

XXX REDO THIS

@@

    \item 5 mails (20 warnings) have out of order log entries, leading to
        warnings about missing data and queueids.  The two log files where
        the out of order log lines occur are more than an order of
        magnitude larger than normal, due to the extremely large volume of
        mail handled by the server on those days; process scheduling
        vagaries and the undefined order of messages sent to syslog(8) may
        explain why the lines were out of order.

@@

The first of these problems cannot be dealt with; although out of order log
lines (the second problem) are dealt with in other circumstances (see
sections~\ref{tracking-re-injected-mail},~\ref{discarding cleanup
lines}~and~\ref{pickup logging after cleanup}), dealing with these lines
would introduce a large amount of complication (deferred warnings, deferred
committal, ambiguity) for a problem which occurs only four times in
60721709 log lines.

The state table contains entries for mails not yet delivered when the
parser finishes execution.  Ideally all it should contain are mails which
are awaiting delivery after the period covered by the logs, though it may
also contain mails from the start of the logs whose initial entries are not
contained in the logs.  Any other entries are evidence of a failure in
parsing or an aberration in the logs.  After parsing the 93 test log files
the state table contains XXX entries, breaking down into:

@@

    \item 1 connection which started only seconds before the logs ended and
        had not completed.

    \item 9 mails which had yet to be delivered due to repeated failures.

    \item 4 mails resulting from the out of order log entries described
        above.

@@

>>>>

At the time of writing the parser is being tested with 93 log files.  There
are 28 warnings produced, but because the parser errs on the side of
producing more warnings rather than fewer those 25 warnings represent only
10 problems:

@@

    \item 7 mails (23 warnings) have out of order log entries, leading to
        warnings about missing data and queueids.  The two log files where
        the out of order log lines occur are more than an order of
        magnitude larger than normal, due to the extremely large volume of
        mail handled by the server on those days; process scheduling
        vagaries and the undefined order of messages sent to syslog(8) may
        explain why the lines were out of order.

@@

The first of these problems cannot be dealt with; although out of order log
lines (the second problem) are dealt with in other circumstances (see
sections~\ref{tracking-re-injected-mail},~\ref{discarding cleanup
lines}~and~\ref{pickup logging after cleanup}), dealing with these lines
would introduce a large amount of complication (deferred warnings, deferred
committal, ambiguity) for a problem which occurs only seven times in
60721709 log lines.

The state tables contain entries for mails not yet delivered when the
parser finishes execution.  Ideally all they should contain are mails which
are awaiting delivery after the period covered by the logs, though they may
also contain mails whose initial entries are not contained in the logs.
Any other entries are evidence of a failure in parsing or an aberration in
the logs.  After parsing the 93 test log files the state tables contain 27
entries, breaking down into:

@@

    \item 2 connections which started only seconds before the logs ended
        and had not completed.

    \item 7 mails which had yet to be delivered due to repeated failures.

    \item 5 mails resulting from the out of order log entries described
        above.

@@

    \item 4 mails present for unknown reasons.
